---
title: "Dataset Merger"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plyr)
library(dplyr)
library(janitor)
library(readxl)
library(tidyverse)
```

## Gallup Dataset

The following dataset includes data for 16 questions, observed in 140+ 
countries in years from 2006 to 2019. For now, I'm proceeding with just data from 2010 and 2019 to adjust the format.

The default output from the Gallup platform is an .xlsx file with a different
sheet for each question. Here, I pivot the dataframes and merge all of them into 
one.

The format of the spreadsheet varies, so here, I breakup exports into 3 categories 
of questions by the types of response, to allow for efficient cleaning:

* yes/no:
  + Corruption in Government
  + Corruption Within Businesses
  + Smile or Laugh
  + Feel Well-Rested
  + Experienced Enjoyment Yesterday
  + Experienced Physical Pain Yesterday
  + Experience Worry Yesterday
  + Experience Stress Yesterday
  + Experience Sadness Yesterday
  + Experience Anger Yesterday
  + ??? Worried About Money

* very_likely/somewhat_likely/not_likely_at_all:
  + Likelihood Stranger Would Return a Lost Bag
  + Likelihood Police Would Return a Lost Bag
  + Likelihood Neighbor Would Return Lost Bag

* value:
  + Positive Experience Index
  + Negative Experience Index

First, create functions for cleaning, pivoting variables, and renaming the columns 
in the dataset.

```{r gallup_clean}
# Read in Excel sheet corresponding to a question

read_gallup <- function(path, question){
  data <- read_excel(path,
                     sheet = question, 
                     skip = 6) %>%
    
    # Make column names simpler
    
    clean_names()
  
  return(data)
}

# Reorder the pivoted columns by year instead of by response type (variable name)

reorder_columns <- function(suffixes, data){
  names_to_order <- map(suffixes, ~ names(data)[grep(paste0("_", .x), names(data))]) %>% unlist
  
  names_id <- setdiff(names(data), names_to_order)
  
  data <- data %>%
    select(all_of(names_id), all_of(names_to_order))
  
  return(data)
}

extra_columns_yes_no = c("demographic", "demographic_value", "dk_rf", "n_size")
response_types_yes_no = c("yes", "no")
extra_columns_likely = c("demographic", "demographic_value", "dk", "refused", "n_size")
response_types_likely = c("very_likely", "somewhat_likely", "not_likely_at_all")
extra_columns_value = c("demographic", "demographic_value", "n_size")
response_types_value = "value"

clean_gallup <- function(path, question, prefix, extra_columns, response_types){
  data <- read_gallup(path, question)
  
  # Store years for reordering purposes
  
  suffixes <- unique(data$time)

  # Pivot the dataframe to have different variables by year
  
  data <- data %>%
    select(!all_of(extra_columns)) %>%
    pivot_wider(names_from = time,
                values_from = all_of(response_types))
  
  # Reorder the pivoted columns by year instead of by response type (variable name)
  
  data <- reorder_columns(suffixes, data)
  
  # Add question prefix to column names
  
  data <- data %>% rename_at(2:ncol(.), ~ paste(prefix, ., sep = "_"))
}
```

Second, create dataframes for each of the 16 questions.

```{r gallup_dataframes}
path1 <- "input_data/GallupAnalytics_Export_yes_no.xlsx"

corrupt_government <- clean_gallup(path1, 
                                   "Corruption in Government", 
                                   "corrupt_government", 
                                   extra_columns_yes_no, 
                                   response_types_yes_no)
corrupt_bussinesses <- clean_gallup(path1, 
                                    "Corruption Within Businesses", 
                                    "corrupt_bussinesses", 
                                    extra_columns_yes_no, 
                                    response_types_yes_no)
smile_laugh <- clean_gallup(path1, 
                            "Smile or Laugh", 
                            "smile_laugh", 
                            extra_columns_yes_no, 
                            response_types_yes_no)
rested <- clean_gallup(path1, 
                       "Feel Well-Rested", 
                       "rested", 
                       extra_columns_yes_no, 
                       response_types_yes_no)
enjoyment <- clean_gallup(path1, 
                          "Experienced Enjoyment Yesterday", 
                          "enjoyment", 
                          extra_columns_yes_no, 
                          response_types_yes_no)
physical_pain <- clean_gallup(path1, 
                              "Experienced Physical Pain Yeste", 
                              "physical_pain", 
                              extra_columns_yes_no, 
                              response_types_yes_no)
worry <- clean_gallup(path1, 
                      "Experience Worry Yesterday", 
                      "worry", 
                      extra_columns_yes_no, 
                      response_types_yes_no)
stress <- clean_gallup(path1, 
                       "Experience Stress Yesterday", 
                       "stress", 
                       extra_columns_yes_no, 
                       response_types_yes_no)
sadness <- clean_gallup(path1, 
                        "Experience Sadness Yesterday", 
                        "sadness", 
                        extra_columns_yes_no, 
                        response_types_yes_no)
anger <- clean_gallup(path1, 
                      "Experience Anger Yesterday", 
                      "anger", 
                      extra_columns_yes_no, 
                      response_types_yes_no)

path2 <- "input_data/GallupAnalytics_full.xlsx"

stranger_return_bag <- clean_gallup(path2, 
                      "Likelihood Stranger Would Retur", 
                      "stranger_return_bag", 
                      extra_columns_likely, 
                      response_types_likely)
police_return_bag <- clean_gallup(path2, 
                      "Likelihood Police Would Return ", 
                      "police_return_bag", 
                      extra_columns_likely, 
                      response_types_likely)
neighbor_return_bag <- clean_gallup(path2, 
                      "Likelihood Neighbor Would Retur", 
                      "neighbor_return_bag", 
                      extra_columns_likely, 
                      response_types_likely)

positive_index <- clean_gallup(path2, 
                      "Positive Experience Index", 
                      "positive_index", 
                      extra_columns_value, 
                      response_types_value)
negative_index <- clean_gallup(path2, 
                      "Negative Experience Index", 
                      "negative_index", 
                      extra_columns_value, 
                      response_types_value)
```

Finally, merge all response variables into one dataset by country.

```{r gallup_merge}
# Create a list of dataframes to merge

indicators <- list(
  # yes/no:
  
  corrupt_government, corrupt_bussinesses, smile_laugh, rested, enjoyment, physical_pain, worry, stress, sadness, anger, 
  
  # likely:
  
  stranger_return_bag, police_return_bag, neighbor_return_bag,
  
  # value:
  
  positive_index, negative_index)

# Perform a full_join on all datsets

gallup_data <- join_all(indicators, by = "geography", type = "full")


```


## Data from Chopik, O’Brien, Konrath, 2017
#### Source: https://journals.sagepub.com/doi/abs/10.1177/0022022116673910

The data is presented in a .docx file, which I converted to an .xlsx and then
pulled out the 3 variables observed in 63 countries:

* Mean Total Empathy
* Mean Perspective Taking
* Mean Empathic Concern

I changed some of the country names in the resulting .xlsx for consistency with
the Gallup dataset to make merging possible.

Here, I merge them with our existing dataset.

### TODO:
According to the paper, data was collected in XXXX.


```{r chopik}
chopik_data <- read_excel("input_data/Chopik.xlsx") %>%
  clean_names()

dataset <- full_join(gallup_data, chopik_data, by = "geography")
```

## Global Preferences Survey
#### Source: https://www.briq-institute.org/global-preferences/download

I downloaded the dataset, which was presented in the .dta format native to Stata. 
It also uses ISO 3166-1 alpha-3 for country names, which I'll convert using package `ISOcodes` for the purpose of merging datasets by full country name.

Convert and merge all variables to our dataset:

### TODO:
Data was collected in XXXX.

```{r gps}
library(ISOcodes)

gps_data <- read_excel("input_data/GPS_country.xlsx")

ISO_3166_1_names <- ISO_3166_1 %>%
  select(Alpha_3, Name, Common_name)


gps_data_iso <- left_join(gps_data, ISO_3166_1_names, by = c("isocode" = "Alpha_3")) 

gps_data_iso <- gps_data_iso %>%
  # Rename isocodes into full country names, using the common name instead of official 
  # if available
  
  mutate(geography = if_else(condition = is.na(Common_name),
                                          Name,
                                          Common_name)) %>%
  
  # Select only the new country name column (geography) and all variables
  
  select(geography, colnames(gps_data_iso)[2:48])
```


```{r}
# Merge with our dataset

dataset_with_gps <- full_join(dataset, gps_data_iso, by = "geography") 

# Identify country rows that did not merge correctly

dataset_discrepancies <- dataset_with_gps %>%
  filter(!(geography %in% dataset$geography)) %>%
  select(geography) %>%
  print()
```


```{r}
# Manually fix country names that did not merge properly by renaming 
# in the original GPS dataset and merging again

```


## Corruption Perceptions Index
#### Source: https://www.transparency.org/en/cpi/

I downloaded a dataset containing CPI scores for ~180 countries from 2006 to 2019.
Put the corresponding years into variable names and merge into our dataset:

```{r cpi}

```

