---
title: "Merged Dataset Guide"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(readxl)
```
# Overview

The `dataset.csv` file contains the merged data by country from the following 7 sources:

- Gallup Analytics (16 questions with data from 2006 to 2020)
- Differences in Empathic Concern and Perspective Taking Across 63 Countries (Chopik et al., 2017; data collected before 2016)
- Global Preferences Survey (data collected in 2012)
- Corruption Perceptions Index (data from 2012 to 2020)
- Civic Honesty Around the Globe (Cohn et al., 2019; data collected between 2013 and 2016)
- Universals and variations in moral decisions (Awad et al., 2020; data collected from 2017 to 2019)
- Reappraisal COVID Baseline Emotion

## Gallup Analytics
Captures 16 variables, broken down by year of observation (various ranges from 2006 to 2020, depending on a question). Values in the columns correspond to the percentages of people answering the following:

* yes/no:
  + `corrupt_government`: Corruption in Government 
  + `corrupt_bussinesses`: Corruption Within Businesses
  + `smile_laugh`: Smile or Laugh
  + `rested`: Feel Well-Rested
  + `enjoyment`: Experienced Enjoyment Yesterday
  + `physical_pain`: Experienced Physical Pain Yesterday
  + `worry`: Experience Worry Yesterday
  + `stress`: Experience Stress Yesterday
  + `sadness`: Experience Sadness Yesterday
  + `anger`: Experience Anger Yesterday

* strongly_disagree/somewhat_disagree/neither/somewhat_agree/strongly_agree:
  + `worry_money`: Worried About Money
  
* very_likely/somewhat_likely/not_likely_at_all:
  + `stranger_return_bag`: Likelihood Stranger Would Return a Lost Bag
  + `police_return_bag`: Likelihood Police Would Return a Lost Bag
  + `neighbor_return_bag`: Likelihood Neighbor Would Return Lost Bag

* value:
  + `positive_index`: Positive Experience Index
  + `negative_index`: Negative Experience Index
  
## Empathy
* 3 variables:
  + `mean_empathic_concern`
  + `mean_perspective_taking`
  + `mean_total_empathy`

## Global Preferences Survey
* variables from `patience` to `europe_east`
* definitions of variables are below:

```{r echo = FALSE}
gps_guide <- read_excel("gps_guide.xlsx")
kable(gps_guide)
```

## Corruption Perceptions Index (data from 2012 to 2020):
* variables: `cpi_score_2012` to `cpi_score_2020`

## Returning lost wallets
* variables: `return_percentage` for each of the 4 experimental conditions: `NoMoney`, `Money`, `BigMoney`, `NoKey`

## Moral preferences in sacrificial dilemmas
* variables `RML` to `Cultural_tigthness_and_looseness` (definitions should be integrated)
* percentages choosing to sacrifice in each scenario variant: `Switch`, `Loop`, `Footbridge`

## Reappraisal COVID Baseline Emotion
* `gratitude`
* `hope`
* `love`
* `inspiration`
* `serenity`
* `fear`
* `anger`
* `sadness`
* `stress`
* `distrust`
* `loneliness`
* `socialconnection`